### 2020-09-03 README.Rmd
we already have neon_export / neon_import!

```{r}
raw_files <- neon_index(table = "brd_countdata-expanded", hash="md5")
raw_files
```

@@

```{r message=FALSE}
write.csv(raw_files, "index.csv")
zip("brd_countdata.zip", raw_files$path)
```

>>>>

```{r}
raw_files <- neon_index(table = "brd_countdata", hash="md5")
raw_files
```

@@

```{r message=FALSE}
write.csv(raw_files, "index.csv")
neon_export("my_neondata.zip", product = "DP1.10003.001")
neon_import("my_neondata.zip")
```
